Exceedance probability comparison for the simplified Naomi model

### 2023-06-16 src/naomi-simple_exceedance/exceedance.Rmd
Should be captioned NUTS!

exceedance_manuscript_plot <- df_wide %>%
  pivot_longer(cols = c("TMB", "aghq"), names_to = "method", values_to = "estimate") %>%
  mutate(
    method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"),
    type = fct_relevel(type, "Second 90", "High incidence")
  ) %>%
  ggplot(aes(x = tmbstan, y = estimate, col = sex)) +
    geom_point(shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#56B4E9", "#999999"), labels = c("Female", "Male")) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    facet_grid(type ~ method) +
    labs(x = "", y = "", col = "Sex") +
    theme_minimal() +
    theme(
      legend.position = "bottom"
    )

>>>>

exceedance_manuscript_plot <- df_wide %>%
  pivot_longer(cols = c("TMB", "aghq"), names_to = "method", values_to = "estimate") %>%
  mutate(
    method = fct_reorg(method, "TMB" = "TMB", "PCA-AGHQ" = "aghq"),
    type = fct_relevel(type, "Second 90", "High incidence")
  ) %>%
  ggplot(aes(x = tmbstan, y = estimate, col = sex)) +
    geom_point(shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#56B4E9", "#999999"), labels = c("Female", "Male")) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    facet_grid(type ~ method) +
    labs(x = "NUTS", y = "", col = "Sex") +
    theme_minimal() +
    theme(
      legend.position = "bottom"
    )
